Extreme Value Statistics Draft 1

### 2022-03-25 Draft_final.Rmd
Auto-saving for chaitanya.arora@edu.bme.hu on branch master from commit 6b7b812

---
Title: Extreme Value Statistics Draft 1
Dataset: Wind
Group: 1
Name: Chaitanya Arora, Diandra Gramma
output:
  pdf_document: default
  html_document: default
---

>>>>

---
Title: Extreme Value Statistics Draft 1
Dataset: Wind
Group: 1
Name: Chaitanya Arora, Diandra Gramma
output:
  html_document: default
  pdf_document: default
---
